% !TEX program = xelatex
\documentclass{resume}
\usepackage{fancyhdr}
\usepackage{linespacing_fix}

\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyfoot[R]{2021.10.25}

\begin{document}

\renewcommand\headrulewidth{0pt}
\name{Hanwen Liao}

\basicInfo{
    \email{hanwen@nyu.edu}\textperiodcentered\
    \phone{(+86) 136-3833-2881}\textperiodcentered\
    \github[Poncirus]{https://github.com/Poncirus}\textperiodcentered\
    \homepage[liaohanwen.com]{https://liaohanwen.com}\textperiodcentered\
    \linkedin[Hanwen Liao]{https://www.linkedin.com/in/hanwen-liao-4043b8196/}
}

\section{Education}
\datedsubsection{\textbf{New York University}, NY, US}{Jan. 2021}
M.S. - Computer Engineering
\datedsubsection{\textbf{Beijing University of Posts and Telecommunications}, Beijing, China}{Jun. 2019}
B.E. - Telecommunication Engineering

\section{Work Experience}
\datedsubsection{\textbf{Yuanfudao}, Beijing, China}{Mar. 2021 -- Sep. 2021}
Software Engineer - Basic R\&D Department, Live Broadcast Center, Data Platform Group
\begin{itemize}[parsep=0.25ex]
    \item Used Doris, Flink, Spark, Iceberg and other tools for big data analysis, completed Java Web development for multiple requirements, and presented data indicators of live broadcast through reports and other forms
    \item Maintained and iterated the data query and visualization tool Redash, which includes support for new data sources, expansion of SQL writing methods, optimization of alarm, and access to ldap login
    \item Token responsible for log collection services based on Netty, completed service suppression
    \item Optimized the problem of log duplication and loss, proposed an optimization plan and led the implementation, and reduced the proportion of problem users from a few thousandths to one ten thousandths
    \item Desiged the protocol for sample reporting of logs and led the implementation of related functions
    \item Intercepted Sentry data in Kafka, classified client crash reason, and analyzed it with other indicators
    \item Completed the migration of client-side millions of QPS logs from Alibaba Log Service to Elasticsearch
\end{itemize}
\datedsubsection{\textbf{Huawei}, Shenzhen, China}{Aug. 2020 -- Dec. 2020}
Software Engineer Intern - 2012 Lab, Central Software Institute, Poincaré Lab
\begin{itemize}[parsep=0.25ex]
    \item Analyzed the function call relationship of Linux kernel and learned the principles of LLVM compilation
    \item Developed variable tracer based on LLVM
\end{itemize}
\datedsubsection{\textbf{Eastcom-BUPT Information Technology Co.,Ltd.}, Beijing, China}{Jun. 2018 -- Aug. 2019}
Software Engineer Intern - ISMP Department
\begin{itemize}[parsep=0.25ex]
    \item Maintained the ISMP with C++ (Integrated Service Management Platform)
    \item Developed the interface module, which encodes and decodes between HTTP message and JSON message
    \item Modified the Lua compiler. Added a new grammar (like annotation in Java) and banned specific variable names by modifing the lexical analyzer of the Lua compiler
    \item Restructured the message distribution method, completed load balancing, and improved availability
    \item Created the interface of ISMP and microservice platform with Golang, which passes JSON message
\end{itemize}

\section{Personal Projects}
\datedsubsection{\textbf{Intelligent Healthcare Project}, Beijing, China}{Oct. 2018 -- Apr. 2019}
Supported by Wireless Communication Center, BUPT
\begin{itemize}[parsep=0.25ex]
    \item Collaborated with a group of graduate students to develop intelligent mattress
    \item Developed server program, which receives data from devices and store it in MySQL database
    \item Built an Android APP, which is able to access data from the server and show with charts using Chart.js
\end{itemize}
\datedsubsection{\textbf{IoT Nodes Embedded Development Project}, Beijing, China}{Jun. 2018 -- Oct. 2018}
Supported by Becstrong Co.,Ltd.
\begin{itemize}[parsep=0.25ex]
    \item Developed IoT node program on STM boards
    \item Built an Android APP to receive data and show with charts
\end{itemize}

\section{Skills}
\begin{itemize}[parsep=0.25ex]
    \item
          \textbf{Program Languages}:
          Java, C/C++, Golang, Python, SQL, Sell Script
    \item
          \textbf{Technologies:}:
          Git, Gerrit, Linux
\end{itemize}

\end{document}
